``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)

knitr.figure_dir <- "figure_1s4_conservation_boxplots_output"
source("shared_code/knitr_common.r")
source("shared_code/flybase.r")
source("shared_code/load_groups.r")
````

# Figure 1 - Figure supplement 4

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## Overview

This plot compares average conservation (phastCon score) for the following gene groups:

 * pre-MBT
 * MBT zygotic active
 * MBT zygotic poised
 * MBT maternal
 * All others

``` {r load_data, include=FALSE}
scores.df <- read.delim("phastcon_scores/phastcon_scores.txt", stringsAsFactors=FALSE, header=TRUE)
txs <- flybase_with_custom_txs()
txs <- merge(txs, scores.df)

create_labeled_group <- function(group_label, tx_ids_list, all.txs) {
  group.df <- subset(all.txs, fb_tx_id %in% tx_ids_list[[group_label]])
  group.df$gene_group <- group_label
  group.df
}

group.list <- list("pre-MBT"=fw_all$fb_tx_id,
                   "MBT zygotic active"=sw_groups$dev_high$fb_tx_id,
                   "MBT zygotic poised"=sw_groups$dev_low$fb_tx_id,
                   "MBT maternal"=sw_groups$maternal$fb_tx_id)
all_groups.txs <- do.call(c, group.list)
group.list <- c(group.list, list("Others"=txs$fb_tx_id[!txs$fb_tx_id %in% all_groups.txs]))

groups.df <- do.call(rbind, lapply(names(group.list), create_labeled_group, group.list, txs))
groups.df$gene_group <- factor(groups.df$gene_group, levels=names(group.list))
```

``` {r make_plot, fig.cap="", fig.width=9, fig.height=5}
g <- ggplot(groups.df, aes(x=gene_group, y=mean_conservation)) + 
     geom_boxplot(fill="#f68c64", outlier.size=1) +
     theme_bw() +
     theme(panel.grid=element_blank(),
           axis.text.y=element_text(size=14),
           axis.text.x=element_text(size=12)) +
     labs(x="", y="Conservation score", title="Figure 1 - Figure Supplement 4")
g
```

``` {r calc_pvalues, include=FALSE}

scores.prembt         <- subset(groups.df, gene_group == "pre-MBT")$mean_conservation
scores.mbt_zyg_active <- subset(groups.df, gene_group == "MBT zygotic active")$mean_conservation
scores.mbt_zyg_poised <- subset(groups.df, gene_group == "MBT zygotic poised")$mean_conservation

pv.prembt_vs_zyg_act <- wilcox.test(scores.prembt, scores.mbt_zyg_active, paired=FALSE)$p.value
pv.prembt_vs_zyg_pos <- wilcox.test(scores.prembt, scores.mbt_zyg_poised, paired=FALSE)$p.value
```

The Wilcox test p-value for pre-MBT versus MBT zygotic active is `r pv.prembt_vs_zyg_act`.

The Wilcox test p-value for pre-MBT versus MBT zygotic poised is `r pv.prembt_vs_zyg_pos`.

``` {r save_pdf, include=FALSE}
pdf(figure_path("conservation_boxplots.pdf"), width=9, height=5)
print(g)
dev.off()
```

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE, comment=NA}
sessionInfo()
````
