``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(Vennerable)

knitr.figure_dir <- "figure_1s2c_compare_prembt_genes_to_known_output"
source("shared_code/knitr_common.r")
````

# Comparison of our identified active pre-MBT genes to other known pre-MBT genes

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

``` {r build_tables, echo=FALSE, message=FALSE, results='hide'}

source("shared_code/load_groups.r")
source("shared_code/flybase.r")

load("flybase/fbidmap.RData")
wids <- read.delim('wieschaus/early_zygotic_fb_ids.txt', stringsAsFactors=F, header=F)$V1
wids.mapped <- unique(as.character(subset(fbidmap, prev_id %in% wids)$fb_gene_id))

genes <- unique(flybase_txs()[, c("fb_symbol", "fb_gene_id")])
genes <- genes[order(genes$fb_symbol), ]
genes$our_first_wave  <- ifelse(genes$fb_gene_id %in% fw_all$fb_gene_id, "Yes", "")
genes$wieschaus_genes <- ifelse(genes$fb_gene_id %in% wids.mapped, "Yes", "")

genes.us_only <- subset(genes, our_first_wave == "Yes" & wieschaus_genes == "")
genes.w_only  <- subset(genes, our_first_wave == "" & wieschaus_genes == "Yes")
genes.w_only$our_second_wave <- ifelse(genes.w_only$fb_gene_id %in% sw_all$fb_gene_id, "Yes", "")

genes.common  <- subset(genes, our_first_wave == "Yes" & wieschaus_genes == "Yes")
````

## Genes in common

There are `r nrow(genes.common)` genes common to both lists:

``` {r common_table, echo=FALSE, message=FALSE, results="asis"}
html_table(genes.common)
````

## Genes only in the Wieschaus list

There are `r nrow(genes.w_only)` genes only in the Wieschaus list:

``` {r w_only_table, echo=FALSE, message=FALSE, results="asis"}
html_table(genes.w_only)
````

## Genes only in our list

There are `r nrow(genes.us_only)` genes only in our first wave list:

``` {r us_only_table, echo=FALSE, message=FALSE, results="asis"}
html_table(genes.us_only)
````

## Venn diagram of active pre-MBT genes and Wieschaus early zygotic genes

``` {r show_venn, echo=FALSE, fig.cap="", fig.width=7, fig.height=7}
v <- Venn(list("pre-MBT active"=as.character(c(fw_groups$paused_later$fb_gene_id, fw_groups$never_paused$fb_gene_id)),
               "Wieschaus early zygotic"=as.character(wids.mapped)))
plot(v)
````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````

