``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)

knitr.figure_dir <- "figure_1s2a_pol_replicate_consistency_output"
source("shared_code/knitr_common.r")
````

# Figure: pre-MBT and MBT Pol II replicate consistency

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## pre-MBT Pol II

Pol II signal at the TSS in replicate 1 vs 2 (pre-MBT wave genes colored):

``` {r build_prembt_pol_plot, echo=FALSE, include=FALSE}

source("shared_code/load_groups.r")

pol_tss.custom <- get(load("step3_check_custom_transcripts_output/pol_tss.custom.RData"))
pol_tss <- rbind(pol_tss.custom, get(load("pol_tss.flybase.RData")))

r1 <- subset(pol_tss, replicate == "r1" & tp == "preMBT")[, c("fb_tx_id", "tss.ratio")]
r2 <- subset(pol_tss, replicate == "r2" & tp == "preMBT")[, c("fb_tx_id", "tss.ratio")]

names(r1)[2] <- "ratio.r1"
names(r2)[2] <- "ratio.r2"

pol.df <- merge(r1, r2)
pol.df$first_wave <- ifelse(pol.df$fb_tx_id %in% fw_all$fb_tx_id, "Yes", "No")

g.pol_prembt <- ggplot(pol.df, aes(x=ratio.r1, y=ratio.r2, color=first_wave)) + 
                geom_point(size=1, alpha=0.5) +
                theme_bw() +
                scale_colour_manual("pre-MBT gene", 
                                    values=c("Yes"="red", "No"="gray70"),
                                    guide=guide_legend(override.aes=list(alpha=1, size=2))) +
                labs(x="Pol II TSS enrichment in replicate 1 (log2)", 
                     y="Pol II TSS enrichment in replicate 2 (log2)",
                     title="Pol II pre-MBT ChIP-seq replicates")
````

``` {r prembt_figure, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="", fig.width=9, fig.height=6}
g.pol_prembt
````

## MBT Pol II

Pol II signal at the TSS in replicate 1 vs 2 (MBT wave genes colored):

``` {r build_mbt_pol_plot, echo=FALSE, include=FALSE}

source("shared_code/load_groups.r")

pol_tss.custom <- get(load("step3_check_custom_transcripts_output/pol_tss.custom.RData"))
pol_tss <- rbind(pol_tss.custom, get(load("pol_tss.flybase.RData")))

r1 <- subset(pol_tss, replicate == "r1" & tp == "MBT")[, c("fb_tx_id", "tss.ratio")]
r2 <- subset(pol_tss, replicate == "r3" & tp == "MBT")[, c("fb_tx_id", "tss.ratio")]

names(r1)[2] <- "ratio.r1"
names(r2)[2] <- "ratio.r2"

pol.df <- merge(r1, r2)
pol.df$first_wave <- ifelse(pol.df$fb_tx_id %in% sw_all$fb_tx_id, "Yes", "No")

g.pol_mbt <- ggplot(pol.df, aes(x=ratio.r1, y=ratio.r2, color=first_wave)) + 
             geom_point(size=1, alpha=0.5) +
             theme_bw() +
             scale_colour_manual("MBT gene", 
                                 values=c("Yes"="red", "No"="gray70"),
                                 guide=guide_legend(override.aes=list(alpha=1, size=2))) +
             labs(x="Pol II TSS enrichment in replicate 1 (log2)", 
                  y="Pol II TSS enrichment in replicate 2 (log2)",
                  title="Pol II MBT ChIP-seq replicates")
````

``` {r mbt_figure, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="", fig.width=9, fig.height=6}
g.pol_mbt
````

``` {r output_pdfs, echo=FALSE, include=FALSE}
pdf(figure_path("pol_replicate_scatterplots.pdf"), width=9, height=6, onefile=T)
print(g.pol_prembt)
print(g.pol_mbt)
dev.off()
````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
