``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)

source("shared_code/metagene_graphs.R")

knitr.figure_dir <- "figure_4c_mnase_metagene_output"
source("shared_code/knitr_common.r")
source("shared_code/flybase.r")
source("shared_code/load_groups.r")
source("shared_code/rdata_common.r")
````

# Figure: MNase metagene plot at MBT

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

We'd like to show the MNase profile of the following gene groups at the MBT stage:

* All first wave
* Second wave maternal

``` {r get_metagene_reads_and_build_plot, echo=FALSE, include=FALSE}


mnase.cov <- get_load(paste0(rdata_base_path(), "/MBT_mnase_1.cov.RData"))

all.txs <- flybase_with_custom_txs()
names(all.txs)[which(names(all.txs) == "end")] <- "stop"

txs.fw  <- subset(all.txs, fb_tx_id %in% fw_all$fb_tx_id)
txs.swm <- subset(all.txs, fb_tx_id %in% sw_groups$maternal$fb_tx_id)

reads.fw  <- get_metagene_reads(mnase.cov, txs.fw,  before_tss=250, after_tss=1000, normalization_target=10000000*150, smooth=51, sample="All first wave")
reads.swm <- get_metagene_reads(mnase.cov, txs.swm, before_tss=250, after_tss=1000, normalization_target=10000000*150, smooth=51, sample="Second wave maternal")

reads.df <- rbind(reads.fw, reads.swm)

reads.df$sample <- factor(reads.df$sample, levels=c("All first wave", "Second wave maternal"))

g <- ggplot(reads.df, aes(x=tss_distance, y=smooth)) +
     geom_line() +
     labs(x="Distance to TSS", y="MNase reads", title="MNase metagene profile") +
     geom_vline(xintercept=0, color="gray50") +
     theme_bw() +
     theme(panel.grid = element_blank()) +
     facet_wrap(~ sample, ncol=1)
````

``` {r show_plot, echo=FALSE, fig.cap="", fig.width=6, fig.height=9}
g
````

``` {r save_pdfs, echo=FALSE, include=FALSE}

pdf(figure_path("mbt_mnase_metagenes.pdf"), width=6, height=9, onefile=T)
print(g)
dev.off()
````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
