``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)
library(plyr)

knitr.figure_dir <- "figure_2c_3a_pol_tbp_metagenes_output"

source("shared_code/knitr_common.r")

````

# Figure: Pol II and TBP metagene plots

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## Pre-normalized enrichment

We'd like to show the following metagene profiles:

* **pre-MBT stage**
    - First wave paused
    - First wave paused later
    - First wave not paused
* **MBT stage**
    - First wave paused
    - First wave paused later
    - First wave not paused
    - Second wave developmental active
    - Second wave developmental poised
    - Second wave maternal (all)
    - Second wave maternal (broad promoters only)

Metagene enrichments were calculated and saved (see [generate_metagene_data_for_all_groups.r](generate_metagene_data_for_all_groups.r)).

``` {r show_gene_counts_table, results="asis"}
load("metagene.df.RData")
html_table(unique(metagene.df[, c("gene_group", "group_size")]))
````

``` {r build_pre_normalized_plot, include=FALSE}


fw.groups <- c("FW Paused", "FW Paused later", "FW Not paused")
sw.groups <- c("SW Dev high", "SW Dev low", "SW Maternal", "SW Maternal (broad)")
all.groups <- c(fw.groups, sw.groups)

metagene.df <- subset(metagene.df, sample %in% c("Pol II", "TBP"))

reads.mbt <- subset(metagene.df, tp == "MBT" & gene_group %in% all.groups)
reads.pre_mbt <- subset(metagene.df, tp == "pre-MBT" & gene_group %in% fw.groups)

reads.df <- rbind(reads.mbt, reads.pre_mbt)

reads.df$tp <- factor(reads.df$tp, levels=c("pre-MBT", "MBT"))

g.pn <- ggplot(reads.df, aes(x=tss_distance, y=smooth, color=as.factor(replicate), linetype=sample)) +
        geom_line() +
        labs(x="Distance to TSS", y="Average enrichment over WCE", title="Pol II and TBP metagenes") +
        scale_linetype_discrete("Factor") +
        scale_colour_discrete("Replicate") +
        geom_vline(xintercept=0, color="gray50") +
        geom_hline(yintercept=2, color="gray50", linetype="dashed") +
        theme_bw() +
        theme(panel.grid = element_blank()) +
        facet_grid(gene_group ~ tp, scales="free_y")
````

``` {r show_pre_normalized_plot, fig.cap="", fig.width=8, fig.height=12}
g.pn
````

## Normalize enrichment

Next, we will select the best replicate for each factor/stage combination and normalize so 1 is the maximum enrichment among the gene groups. Based on the above plot, the best replicates are:

* **Pol II**
    * **pre-MBT**: replicate 2
    * **MBT**: replicate 3
* **TBP**
    * **pre-MBT**: replicate 2
    * **MBT**: replicate 2

``` {r calc_max_enrichments, comment=NA, results="asis"}

# Filter for best replicates

reads.pol.pre_mbt <- subset(reads.df, tp == "pre-MBT" & sample == "Pol II" & replicate == 2)
reads.pol.mbt     <- subset(reads.df, tp == "MBT"     & sample == "Pol II" & replicate == 3)

reads.tbp.pre_mbt <- subset(reads.df, tp == "pre-MBT" & sample == "TBP"    & replicate == 2)
reads.tbp.mbt     <- subset(reads.df, tp == "MBT"     & sample == "TBP"    & replicate == 2)

reads.df <- rbind(reads.pol.pre_mbt, reads.pol.mbt, reads.tbp.pre_mbt, reads.tbp.mbt)

max.enrichments <- ddply(reads.df, .(tp, sample), summarize, max_enrichment      = max(smooth), 
                                                             found_in_gene_group = gene_group[which.max(smooth)],
                                                             found_at_location   = tss_distance[which.max(smooth)])
html_table(max.enrichments)
````

``` {r normalize_enrichments_and_build_plot, fig.cap="", fig.width=8, fig.height=9}
reads.df <- merge(reads.df, max.enrichments[, c("tp", "sample", "max_enrichment")])

reads.df <- transform(reads.df, normalized_enrichment = smooth / max_enrichment)

reads.df$tp <- factor(reads.df$tp, levels=c("pre-MBT", "MBT"))

g.n <- ggplot(reads.df, aes(x=tss_distance, y=normalized_enrichment, color=sample)) +
       geom_line() +
       labs(x="Distance to TSS", y="Normalized enrichment", title="Pol II and TBP metagenes (normalized)") +
       scale_colour_discrete("Factor") +
       geom_vline(xintercept=0, color="gray50") +
       scale_y_continuous(breaks=c(0, 1), labels=c("Min", "Max")) +
       theme_bw() +
       theme(panel.grid = element_blank()) +
       facet_grid(gene_group ~ tp)
g.n
````

The following table shows the location of maximum enrichment for each panel and factor:

``` {r location_of_maximums_table, results="asis"}

all.maxes <- ddply(reads.df, .(gene_group, tp, sample), summarize, max_enrichment    = max(smooth), 
                                                                   found_at_location = tss_distance[which.max(smooth)])

html_table(all.maxes)
````

``` {r save_pdfs, include=FALSE}

pdf(figure_path("pol_tbp_metagenes_enrichment.pdf"), width=8, height=12, onefile=T)
print(g.pn)
dev.off()

pdf(figure_path("pol_tbp_metagenes_normalized.pdf"), width=8, height=12, onefile=T)
print(g.n)
dev.off()

# log2 normalized
reads.log2 <- transform(reads.df, normalized_enrichment = log2(smooth) / log2(max_enrichment))

g.log2 <- ggplot(reads.log2, aes(x=tss_distance, y=normalized_enrichment, color=sample)) +
          geom_line() +
          labs(x="Distance to TSS", y="Normalized enrichment (log2)", title="Pol II and TBP metagenes (normalized, log2)") +
          scale_colour_discrete("Factor") +
          geom_vline(xintercept=0, color="gray50") +
          scale_y_continuous(breaks=c(0, 1), labels=c("Min", "Max")) +
          theme_bw() +
          theme(panel.grid = element_blank()) +
          facet_grid(gene_group ~ tp)

pdf(figure_path("pol_tbp_metagenes_normalized_log2.pdf"), width=8, height=9, onefile=T)
print(g.log2)
dev.off()


````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info}
sessionInfo()
````
