``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)

knitr.figure_dir <- "figure_5b_meme_results_output"

source("shared_code/knitr_common.r")
source("shared_code/meme_xml.r")

meme.prembt <- parse_meme_xml("meme/prembt_active/meme.xml")
meme.mbt    <- parse_meme_xml("meme/mbt_active/meme.xml")
````

# Figure: MEME results

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## pre-MBT active genes

`r pn(meme.prembt$sequence_count)` genes were analyzed with MEME as part of the pre-MBT active set. 

``` {r prembt_meme_figures, warning=FALSE, message=FALSE, fig.cap=""}


seq_logo_and_site_histogram <- function(meme, motif) {
  seqLogo(meme$motifs[[motif]])
  g <- ggplot(meme$motif_sites[[motif]], aes(x=position-125)) + 
       geom_histogram() +
       #geom_line(stat="density") +
       xlim(-125, 125) +
       theme_bw() +
       labs(x="Position relative to TSS", title=sprintf("%s\n%s sites", motif, meme$motif_info[[motif]]$sites))
  print(g)
}


for(motif in names(meme.prembt$motifs)) {
  seq_logo_and_site_histogram(meme.prembt, motif)
}

````

## MBT active genes

`r pn(meme.mbt$sequence_count)` genes were analyzed with MEME as part of the MBT active set. 

``` {r mbt_meme_figures, warning=FALSE, message=FALSE, fig.cap=""}

seq_logo_and_site_histogram <- function(meme, motif) {
  seqLogo(meme$motifs[[motif]])
  g <- ggplot(meme$motif_sites[[motif]], aes(x=position-125)) + 
       geom_histogram() +
       #geom_line(stat="density") +
       xlim(-125, 125) +
       theme_bw() +
       labs(x="Position relative to TSS", title=sprintf("%s\n%s sites", motif, meme$motif_info[[motif]]$sites))
  print(g)
}


for(motif in names(meme.mbt$motifs)) {
  seq_logo_and_site_histogram(meme.mbt, motif)
}

````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
