``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(ggplot2)
library(plyr)

knitr.figure_dir <- "figure_4c_pol_k4_metagenes_output"
source("shared_code/knitr_common.r")
````

# Figure: Pol II and K4me3 metagene plots

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## Pre-normalized enrichment

We'd like to show the following metagene profiles:

* **MBT stage**
    - All first wave 
    - Second wave maternal

Metagene enrichments were calculated and saved (see [generate_metagene_data_for_all_groups.r](generate_metagene_data_for_all_groups.r)).

``` {r build_pre_normalized_plot, echo=FALSE, include=FALSE}

load("metagene.df.RData")

fw.groups <- c("FW All")
sw.groups <- c("SW Maternal")

all.groups <- c(fw.groups, sw.groups)

metagene.df <- subset(metagene.df, sample %in% c("Pol II", "K4"))
reads.df <- subset(metagene.df, tp == "MBT" & gene_group %in% all.groups)

reads.df$sample <- factor(reads.df$sample, levels=c("Pol II", "K4"))

g <- ggplot(reads.df, aes(x=tss_distance, y=smooth, color=as.factor(replicate))) +
     geom_line() +
     labs(x="Distance to TSS", y="Average enrichment over WCE", title="Pol II and K4me3 metagenes") +
     scale_colour_discrete("Replicate") +
     geom_vline(xintercept=0, color="gray50") +
     theme_bw() +
     theme(panel.grid = element_blank()) +
     facet_grid(gene_group ~ sample, scales="free_y")
````

``` {r show_pre_normalized_plot, echo=FALSE, fig.cap="", fig.width=8, fig.height=9}
g
````

## Normalize enrichment

Next, we will select the best replicate for each factor and normalize so 1 is the maximum enrichment among the gene groups. Based on the above plot, the best replicates are:

* **Pol II**: replicate 3
* **K4**: replicate 2

``` {r calc_max_enrichments, echo=FALSE, comment=NA, results="asis"}

# Filter for best replicates

reads.pol.mbt <- subset(reads.df, sample == "Pol II" & replicate == 3)
reads.k4.mbt  <- subset(reads.df, sample == "K4"     & replicate == 2)

reads.df <- rbind(reads.pol.mbt, reads.k4.mbt)

max.enrichments <- ddply(reads.df, .(sample), summarize, max_enrichment      = max(smooth), 
                                                         found_in_gene_group = gene_group[which.max(smooth)],
                                                         found_at_location   = tss_distance[which.max(smooth)])
html_table(max.enrichments)
````

``` {r normalize_enrichments_and_build_plot, echo=FALSE, fig.cap="", fig.width=8, fig.height=9}
reads.df <- merge(reads.df, max.enrichments[, c("sample", "max_enrichment")])

reads.df <- transform(reads.df, normalized_enrichment = smooth / max_enrichment)

reads.df$sample <- factor(reads.df$sample, levels=c("Pol II", "K4"))

g.n <- ggplot(reads.df, aes(x=tss_distance, y=normalized_enrichment, color=sample)) +
       geom_line() +
       labs(x="Distance to TSS", y="Normalized enrichment", title="Pol II and K4me3 metagenes (normalized)") +
       scale_colour_discrete("Factor") +
       geom_vline(xintercept=0, color="gray50") +
       scale_y_continuous(breaks=c(0, 1), labels=c("Min", "Max")) +
       theme_bw() +
       theme(panel.grid = element_blank()) +
       facet_wrap(~ gene_group, ncol=1)
g.n
````

``` {r save_pdfs, echo=FALSE, include=FALSE}

pdf(figure_path("pol_k4_metagenes_enrichment.pdf"), width=8, height=9, onefile=T)
print(g)
dev.off()

pdf(figure_path("pol_k4_metagenes_normalized.pdf"), width=8, height=9, onefile=T)
print(g.n)
dev.off()

````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
