``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(GenomicRanges)
library(BSgenome.Dmelanogaster.UCSC.dm3)

knitr.figure_dir <- "meme_analysis_prembt_vs_mbt_output"

source("shared_code/knitr_common.r")
source("shared_code/flybase.r")
source("shared_code/load_groups.r")
````

# MEME analysis of pre-MBT active and MBT active gene groups

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

## Gene groups

We will output the promoter sequences (250bp centered at the TSS) for the following groups of genes:

 * **pre-MBT** active: all pre-MBT genes except the pre-MBT paused group
 * **MBT active**: MBT active group only

``` {r gene_groups, results='asis'}
txs <- flybase_with_custom_txs_granges()
txs <- resize(txs, width=1,   fix="start")
txs <- resize(txs, width=250, fix="center")

prembt.txs <- c(fw_groups$paused_later$fb_tx_id, fw_groups$never_paused$fb_tx_id)
mbt.txs    <- c(sw_groups$dev_high$fb_tx_id)

group.prembt <- txs[values(txs)$fb_tx_id %in% prembt.txs]
group.mbt    <- txs[values(txs)$fb_tx_id %in% mbt.txs]

html_table(data.frame(gene_group=c("pre-MBT active", "MBT active"), size=pn(c(length(group.prembt), length(group.mbt)))))
````

These promoter sequences will be written to two FASTA files:

 * meme/prembt\_active.fasta
 * meme/mbt\_active.fasta

``` {r output_fasta, include=FALSE}

seq.prembt <- getSeq(Dmelanogaster, group.prembt)
seq.mbt    <- getSeq(Dmelanogaster, group.mbt)

names(seq.prembt) <- with(values(group.prembt), sprintf("%s(%s)", fb_gene_id, fb_symbol))
names(seq.mbt)    <- with(values(group.mbt),    sprintf("%s(%s)", fb_gene_id, fb_symbol))

writeXStringSet(seq.prembt, filepath="meme/prembt_active.fasta")
writeXStringSet(seq.mbt,    filepath="meme/mbt_active.fasta")
````

``` {r meme_command, engine="bash", echo=TRUE, eval=FALSE}
MEME=$HOME/apps/meme/bin/meme

$MEME meme/prembt_active.fasta -mod zoops -dna -nmotifs 25 -revcomp -maxw 12 -maxsize 5000000 -oc meme/prembt_active
$MEME meme/mbt_active.fasta    -mod zoops -dna -nmotifs 25 -revcomp -maxw 12 -maxsize 5000000 -oc meme/mbt_active
````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
