``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)
library(plyr)
library(reshape)

knitr.figure_dir <- "step6_select_second_wave_genes_by_tss_output"

source("shared_code/knitr_common.r")
````

# Step 6: Selecting second wave genes by Pol II TSS enrichment

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

After calculating Pol II enrichment in the TSS and TU regions ([pol_enrichments_flybase.r](pol_enrichments_flybase.r)) for all three MBT samples, we can now define those genes that have Pol II bound in the second wave of zygotic genome activation.

We will use the following criteria to define an initial list of transcripts based on Flybase annotations:

* Enrichment at least 2-fold above background in the TSS region in all three replicates
* Genes already selected as first wave genes will be excluded

``` {r pol_tss_calculations, echo=FALSE, message=FALSE}

source("shared_code/tss_tu_summary.r")
source("shared_code/flybase.r")

pol_tss <- get(load("pol_tss.flybase.RData"))
pol_tss <- subset(pol_tss, tp == "MBT")

counts.df <- summarize_tss_tu_values(pol_tss, flybase_txs())

df <- subset(counts.df, tss_count == 3)

# Select transcript with maximum mean TSS/TU ratio for tss.wide
message("Selecting 1 tx per gene")
tss.selected_tx <- as.character(ddply(df, .(fb_gene_id), summarize, 
                                      fb_tx_id=fb_tx_id[order(min_tss_signal_quantile, mean_tu, decreasing=TRUE)[1]])$fb_tx_id)

df$highest_tss <- df$fb_tx_id %in% tss.selected_tx
sw.df <- subset(df, tss_count == 3 & highest_tss == TRUE)

# Remove first wave genes

fw.genes <- as.character(get(load("step4_final_first_wave_gene_list_output/fw.df.RData"))$fb_gene_id)
sw.df <- subset(sw.df, ! fb_gene_id %in% fw.genes)

save(sw.df, file=figure_path("sw.df.RData"))
write.table(sw.df, file=figure_path("second_wave_genes_by_tss.xls"), quote=F, sep="\t", row.names=F, col.names=T)
````

This yields `r pn(nrow(sw.df))` second wave genes.

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
