``` {r setup, echo=FALSE, message=FALSE, results="hide"}
library(xtable)

knitr.figure_dir <- "step5_classifying_first_wave_genes_output"

source("shared_code/knitr_common.r")
source("shared_code/load_groups.r")
source("shared_code/flybase.r")

````

# Step 5: Classifying first wave genes

**Project:** `r knitr.project_name`

**Author:** [Jeff Johnston](mailto:jjj@stowers.org)

**Generated:** `r format(Sys.time(), "%a %b %d %Y, %I:%M %p")`

We classify the first wave genes into 3 groups:

 * **Paused**: those with a mean Pol II TU enrichment of less than 0 (log2)
 * **Paused later**: those not paused during pre-MBT but having Pol II TSS enrichment in the top 20% in 6-8h sorted muscle cells
 * **Never paused**: all the remaining genes

``` {r fw_count_table, echo=FALSE, comment=NA, results='asis'}
fw_table <- data.frame(stringsAsFactors=F, group_name=names(fw_groups), gene_count=sapply(fw_groups, nrow))
html_table(fw_table)
````

## Paused

``` {r fw_paused_table, echo=FALSE, comment=NA, results='asis'}
html_table(fw_groups$paused)
````

## Paused later

``` {r fw_paused_later_table, echo=FALSE, comment=NA, results='asis'}
html_table(fw_groups$paused_later)
````

## Never paused

``` {r fw_never_paused_table, echo=FALSE, comment=NA, results='asis'}
html_table(fw_groups$never_paused)
````

``` {r output_spreadsheet, echo=FALSE, include=FALSE}
add_name_to_group <- function(group_name, groups) {
  df <- groups[[group_name]]
  df$classification <- group_name
  df
}

fw.dfs <- lapply(names(fw_groups), function(x) { add_name_to_group(x, fw_groups)})
fw.dfs <- do.call(rbind, fw.dfs)
fw.dfs <- fw.dfs[order(fw.dfs$classification, fw.dfs$fb_symbol), ]
write.table(fw.dfs, file=figure_path("first_wave_genes_classified.xls"), quote=F, sep="\t", row.names=F, col.names=T)

all.txs <- flybase_with_custom_txs()
fw.txs <- merge(all.txs, fw.dfs[, c("fb_tx_id", "classification")])
write.table(fw.txs, file=figure_path("first_wave_genes_classified_with_coordinates.xls"), quote=F, sep="\t", row.names=F, col.names=T)
````

## Session information

For reproducibility, this analysis was performed with the following R/Bioconductor session:

``` {r session_info, echo=FALSE}
sessionInfo()
````
